Artificial Intelligence Course Report

### 2018-01-14 paper/Zhenghui/paper.tex
figs

\begin{itemize}
	\item \textbf{NN on PCA-processed data}\\
	In this model, firstly we use pca-processed data (500-dimension) as our network input. Then we add hidden layer1(256-dimension), hidden layer2(512-dimension), hidden layer3(256-dimension), finally a output layer.  The structure is shown as Figure~\ref{nn_1} network \romannumeral1. 
	For weight initialization, we initialize each neurons weight vector as a random vector sampled from a multi-dimensional gaussian. For bias initialization, we set the bias vectors all to $0$. We initialize our weight with the consideration that the size of our network is limited and it can be trained easily according to the network \romannumeral2.

@@

\begin{figure}[]
	\centering
	\includegraphics[width=0.24\textwidth,height=3cm]{../figs/pretrain1.png}
	\includegraphics[width=0.24\textwidth,height=3cm]{../figs/pretrain2.png}
	\includegraphics[width=0.24\textwidth,height=3cm]{../figs/pretrain3.png}
	\includegraphics[width=0.24\textwidth,height=3cm]{../figs/pretrain4.png}
	\caption{a.network \romannumeral1;  b, network \romannumeral2; c, network \romannumeral3; d, network \romannumeral4}
	\label{pretrain_1}
	\centering
\end{figure}

@@

	\begin{figure}[]
		\centering
		\includegraphics[width=0.4\textwidth]{../figs/Material-2.pdf}
		\includegraphics[width=0.4\textwidth]{../figs/Sex-2.pdf}
		\includegraphics[width=0.4\textwidth]{../figs/Disease-16.pdf}
		\includegraphics[width=0.4\textwidth]{../figs/Bio-7.pdf}
		\caption{a.Material-2 Distribution;  b, Sex-2 Distribution2; c, Disease-16 Distribution; d,Bio-7 Distribution}
		\label{distribution_1}
		\centering
	\end{figure}

@@

\subsection{Deep Learning based Method}

\subsubsection{ NN on PCA-processed data}
At first we try deep neural network on   pca-processed data. The dimension is 500, and the network is shown in Figure~\ref{nn_1}. Besides,  we use L2 regularization and dropout to avoid overfitting. The dropout rate is 0.50. In the end, we use batch normalization in each layer and it greatly improves the performance. The results and selected parameters are shown in Table~\ref{nnpca_result}.

@@

		\caption{Best results and parameter settings for nn model on pca data. }
		\label{nnpca_result}
	\end{table}

@@

	\begin{figure}[]
		\centering
		\includegraphics[width=0.4\textwidth]{../figs/lr_acc_bio.pdf}
		\includegraphics[width=0.4\textwidth]{../figs/lr_acc_sex.pdf}
		\includegraphics[width=0.4\textwidth]{../figs/lr_loss_bio.pdf}
		\includegraphics[width=0.4\textwidth]{../figs/lr_loss_sex.pdf}
		\caption{a.accuracy in Bio task;  b, accuracy in Sex task; c, loss in Bio task; d, loss in Sex task}
		\label{lr_result}
		\centering
	\end{figure}

>>>>

\begin{itemize}
	\item \textbf{NN on PCA-processed data}\\
	In this model, firstly we use PCA-processed data (500-dimension) as our network input. Then we add hidden layer1(256-dimension), hidden layer2(512-dimension), hidden layer3(256-dimension), finally a output layer.  The structure is shown as Figure~\ref{nn_1} network \romannumeral1. 
	For weight initialization, we initialize each neurons weight vector as a random vector sampled from a multi-dimensional gaussian. For bias initialization, we set the bias vectors all to $0$. We initialize our weight with the consideration that the size of our network is limited and it can be trained easily according to the network \romannumeral2.

@@

\begin{figure}[]
	\centering
	\includegraphics[width=0.2\textwidth]{../figs/pretrain1.png}
	\includegraphics[width=0.2\textwidth]{../figs/pretrain2.png}
	\includegraphics[width=0.2\textwidth]{../figs/pretrain3.png}
	\includegraphics[width=0.2\textwidth]{../figs/pretrain4.png}
	\caption{a.network \romannumeral1;  b, network \romannumeral2; c, network \romannumeral3; d, network \romannumeral4 (From left to right and top to down). }
	\label{pretrain_1}
	\centering
\end{figure}

@@

	\begin{figure}[]
		\centering
		\includegraphics[width=0.2\textwidth]{../figs/Material-2.pdf}
		\includegraphics[width=0.2\textwidth]{../figs/Sex-2.pdf}
		\includegraphics[width=0.2\textwidth]{../figs/Disease-16.pdf}
		\includegraphics[width=0.2\textwidth]{../figs/Bio-7.pdf}
		\caption{a.Material-2 Distribution;  b, Sex-2 Distribution2; c, Disease-16 Distribution; d,Bio-7 Distribution (From top to down). }
		\label{distribution_1}
		\centering
	\end{figure}

@@

\subsection{Deep Neural Network}

\subsubsection{ NN on PCA-processed data}
At first we try deep neural network on   PCA-processed data. The dimension is 500, and the network is shown in Figure~\ref{nn_1}. Besides,  we use L2 regularization and dropout to avoid overfitting. The dropout rate is 0.50. In the end, we use batch normalization in each layer and it greatly improves the performance. The results and selected parameters are shown in Table~\ref{nnpca_result}.

@@

		\caption{Best results and parameter settings for NN model on PCA data. }
		\label{nnpca_result}
	\end{table}

@@

	\begin{figure}[]
		\centering
		\includegraphics[width=0.2\textwidth]{../figs/lr_acc_bio.pdf}
		\includegraphics[width=0.2\textwidth]{../figs/lr_acc_sex.pdf}
		\includegraphics[width=0.2\textwidth]{../figs/lr_loss_bio.pdf}
		\includegraphics[width=0.2\textwidth]{../figs/lr_loss_sex.pdf}
		\caption{a.accuracy in Bio task;  b, accuracy in Sex task; c, loss in Bio task; d, loss in Sex task (From left to right and top to down). }
		\label{lr_result}
		\centering
	\end{figure}
